### 2014-03-05 seminar/seminar_report/Abstract.tex
changes

In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. There are a number of proposed mechanisms and models on aggregating web services and making them cooperate within their communities. However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet. Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests, but also exhibit cooperative behaviors, for instance in terms of substituting each other.

In this report, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose preliminary results using cooperative game-theoretic techniques. We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities. The ultimate objective is to develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world like environments, with applicable and near-optimal decision making mechanisms. We also propose a decision mechanism based on learning methods for services within communities to effectively choose the tasks to perform based on their capabilities and the competition between other community members.

>>>>

In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. There are a number of proposed mechanisms and models on aggregating web services and making them cooperate within their communities. However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet. Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests. However, those services can also exhibit cooperative behaviors, for instance in terms of substituting each other. Deciding to compete or cooperate inside communities is a problem yet to be investigated.

In this report, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose some results using cooperative game-theoretic techniques. We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities. The ultimate objective is to develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities. The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world like environments, with applicable and near-optimal decision making mechanisms. We also propose a decision mechanism based on learning methods for services within communities to effectively choose the tasks to perform based on their capabilities and the competition between other community members.

### 2014-03-05 seminar/seminar_report/chapter1.tex
changes

Web service communities are dynamic by design
\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
services are modeled as intelligent autonomous agents, where they
can adopt a strategy maximizing their payoff at any time. A web
service can ask joining a community and has the right to leave it.
Community managers can invite or ask a web service to leave in
order to maximize the community profit. Users can simply stop
sending requests to a web service which is not providing
satisfactory services. Thus its important to consider all the
parties involved in the decision making process about the
community management.

@@

Within communities, service providers can 
can have competitive behaviour as they provide the same functionalities and the number of users requests is finite. So as an extension to our work, we have implemented a framework in which service providers can opt for performing tasks if they feel they are capable enough.
We have implemented an online learning mechanism for service providers with different captaincies to learn over time which strategy to choose based on their own and other service providers status and capabilities. After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (q-learning) techniques.

\indent To summarize, the main problem we aim to tackle in this
thesis is the formation of stable and efficient coalitions
maximizing web services and community revenue. The main objectives
are:
\begin{itemize}
\item To propose a cooperative model and analyze its solution
concepts in order to address the problem of optimizing coalition
formation for a stable community.

@@

\section{Report Organization}\label{sec:outline}
The rest of the report is organized as follows: We present in
Chapter~\ref{sec:MAS} the background needed for our research along
with relevant related work. Chapter~\ref{sec:coalitionformationws}
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter~\ref{sec:conclusionfuturework}, we present our conclusion,
future plan, and the timetable of our research.

>>>>

Web service communities are dynamic by design
\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
services are modeled as intelligent autonomous agents, where they
can adopt a strategy maximizing their payoff at any time. A web
service can ask joining a community and has the right to leave it.
Community managers can invite or ask a web service to leave in
order to maximize the community profit. Users can simply stop
sending requests to a web service which is not providing
satisfactory services. Thus it is important to consider all the
parties involved in the decision making process about the
community management.

@@

Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
or decide to cooperate by showing the availability to perform some sub-tasks.
We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities. After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (Q-learning) techniques.

\indent To summarize, the main problems we aim to tackle in this
thesis are the formation of stable and efficient coalitions
maximizing web services and community revenue and the decision over the strategy to play about competing or cooperating.
The main objectives are:
\begin{itemize}
\item To propose a cooperative model and analyze its solution
concepts in order to address the problem of optimizing coalition
formation for a stable community.

@@

\section{Report Organization}\label{sec:outline}
The rest of the report is organized as follows. We present in
Chapter~\ref{sec:MAS} the background needed for our research along
with relevant related work. Chapter~\ref{sec:coalitionformationws}
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter~\ref{sec:conclusionfuturework}, we present our conclusion,
future plan, and the timetable of our research.

### 2014-03-05 seminar/seminar_report/chapter2.tex
changes

In this chapter then we introduce
the concept of communities of web services, their architecture and
applications and the benefits of forming communities. Thereafter,
we discuss the cooperative game theory concepts used throughout
the proposal. Finally, we discuss relevant related work on web
service communities and games in the literature of service
oriented computing.

@@

Alternatively, the $\epsilon$ can be thought of as a \emph{tax} imposed on a coalition should it choose to deviate. This can again be seen as an external party, trying to stabilize the coalition by imposing some \emph{tax} on deviation. Taxation and subsiding as methods of stabilizing cooperative games have been studied in \cite{RePEc:spr:jogath:v:38:y:2009:i:1:p:3-16, Bachrach:2009:CSC:1692490.1692502, conf/ijcai/MeirRM11}.

>>>>

In this chapter we introduce
the concept of communities of web services, their architecture and
applications and the benefits of forming such communities. Thereafter,
we discuss the cooperative game theory concepts used throughout
the proposal. Finally, we discuss relevant related work on web
service communities and games in the literature of service
oriented computing.

@@

Alternatively, $\epsilon$ can be thought of as a \emph{tax} imposed on a coalition should it choose to deviate. This can again be seen as an external party, trying to stabilize the coalition by imposing some \emph{tax} on deviation. Taxation and subsiding as methods of stabilizing cooperative games have been studied in \cite{RePEc:spr:jogath:v:38:y:2009:i:1:p:3-16, Bachrach:2009:CSC:1692490.1692502, conf/ijcai/MeirRM11}.

### 2014-03-05 seminar/seminar_report/chapter3.tex
changes

\chapter{Coalition Formation for Autonomous Web Services}\label{sec:coalitionformationws}

In this chapter, we present our coalition model of agent-based web
services within communities\cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with
some simulation results.

@@

Web services come with different quality of service parameters.
These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}.
We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain linear weight function of the parameters. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

@@

While distributing tasks, the community master can verify the performance, throughput and quality of service of   tasks being performed by web services. It can recognize if web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations but also to penalize them.
In this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may  degrade or improve, a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools. Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

\section{Competitive behaviour of services within communities}\label{s:coop}

In previous sections, our focus was on community formation and we emphasised on cooperative behaviour of the web services as agents. Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this paper interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

\subsection{The Proposed Framework}\label{The Proposed Framework}
In this section, we first present the architecture of the proposed
model. We explore the characteristics of intelligent service
agents and their network. We link this architecture to the
implemented system where we investigate the services' coopetitive
attitudes. We compute the involved system parameters and explain
the services' interactive strategy profiles by highlighting their
coopetitive choices.

@@

\subsubsection{The Architecture}

@@

\subsubsection{System Parameters}
In this section, we demonstrate the involved parameters and their
corresponding formulations and explanations.

@@

\subsubsection{Service Interactive Strategies}

The main goal of each individual service agent is to increase its
income (payoff). This income can be earned from tasks (or
requests) done by this service. In our model, services can decide
to compete to get a task from the master agent or to cooperate
with other services within a given collaborative network (the way
a collaborative network is set by a leader is based on the
cooperative services reputation and their QoS parameters that
should coincide with the required QoS). Therefore we define two
types of service strategies. First, when a service has higher
level of confidence based on its growth factor, it can compete to
get a task from the master and adopts the competitive strategy.
Second, when the service agent has a lower level of confidence
that it does not feel capable to compete, it waits for some other
services to cooperate with to perform some tasks \footnote{Through
the paper, requests or tasks are supposed to be decomposable.},
and thus it adopts the cooperative strategy. Services estimate the
outcome of all the strategies and choose one of them accordingly.
This decision is not static but can change over time so service
agents can switch from one strategy to the other, and this dynamic
attitude is referred to as coopetition.

@@

@@

For the \emph{optimal core} method, we have used the well known
\emph{$\epsilon$-core} method as the taxation method to relax the
core condition to help communities attract web services. We have
assigned $\epsilon$ to 15\% of total community worth, which means
$\epsilon = 0.15 \times v(C)$. This allows subsets of the
coalition to gain maximum 15\% of $v(C)$.
%In the \emph{optimal
%$\epsilon$-core} method, we capped the coalition size to 25 web
%services, since the method is computationally intractable as the
%number of web services increases. In fact, given the machine
%configuration we used in our experiments, the maximum number we
%could run for this method is 25, which is very realistic if we
%consider the real airlines coalitions (the three well known
%coalitions have respectively 28, 19, and 13 members). In the other
%methods, there were no cap on size of the community and we had
%communities of size 160 web services at some points, as discussed
%above.
In the experiments, our \emph{Depth-1 Convex-Checker} and
\emph{Depth-2 Convex-Checker} methods generate results instantly
(0.01ms in Java millisecond time unit granularity) in our machines
since their runtime with respect to the size of input (number of
web services) is $O(n)$ and $O(n^2)$ respectively. This shows that
the algorithms are efficient and the system is easily scalable. In
this scenario, our community receives 130 tasks from users on
average per iteration. These tasks are about flight booking and
are expected to be performed by the community. They are randomly
generated using a poisson distribution (having 130 as parameter).
Depending on community task queue and the assigned web services'
quality metrics the task will be performed with some qualities.
The community, after the task distribution process on each
iteration, will reevaluate QoS metrics of its members and can
check for new membership requests. Web services may join or leave
the community between iterations. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to the optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing
well.

@@

\subsection*{Coopetitive behaviour of services within communities}\label{sb:resutlscoop}

In this section, the objective is to investigate the effectiveness of the proposed strategic system in section \ref{s:coop}.
We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this report (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive).
%The proposed model's
%reasoning mechanism allows services to make decisions that
%maximize their utilities, so that if the service cannot compete,
%the procedure would suggest to collaborate, which is better than
%competing and failing to obtain the task. In this case, the service stays idle but
%still pays the community membership fee, which means losing
%utility. The developed strategic decision making mechanism leads
%some service agents to follow cooperative strategies that overall
%maintain an optimal community budget. In the same figure, we
%observe the cumulative budget of a community where services follow
%random interacting strategies. The outcome is clearly lower
%because services at each run randomly decide over their acting
%strategies. This potentially influences the community budget
%because a low quality service if randomly selects to follow the
%competitive strategy, it will fail to perform a task with high QoS
%requirements.

>>>>

\chapter{Coalition Formation and Coopetitive Behavior of Autonomous Web Services}\label{sec:coalitionformationws}

In this chapter, we present our coalition model of agent-based web
services within communities \cite{SCC2013efficient}. We start by describing the general
architecture and considered parameters for web services.
Thereafter, problem modeling and formulation will be introduced in
terms of task distribution and community revenue. Web service
cooperative games in different settings will follow along with
some simulation results.

@@

Web services come with different quality of service parameters.
These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security \cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented environment includes the QWS dataset by Eyhab Al-Masri and Qusay H. Mahmoud freely available at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}.
We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain linear weight function of the parameters. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

@@

While distributing tasks, the community master can verify the performance, throughput and quality of service of   tasks being performed by web services. It can recognize if web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations. 
Web services that got their quality declined are penalized, and in this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may  degrade or improve, a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools. Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. The used
algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

\section{Coopetitive Behavior of Services within Communities}\label{s:coop}

In previous sections, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents. Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

%\subsection{The Proposed Framework}\label{The Proposed Framework}
Here, we first present the architecture of the proposed
model. We explore the characteristics of intelligent service
agents and their network. We link this architecture to the
implemented system where we investigate the services' coopetitive
attitudes. We compute the involved system parameters and explain
the services' interactive strategy profiles by highlighting their
coopetitive choices.

@@

\subsection{Architecture}

@@

\subsection{System Parameters}
In this section, we demonstrate the involved parameters and their
corresponding formulations and explanations.

@@

\subsection{Service Interactive Strategies}

The main goal of each individual service agent is to increase its
income (payoff). This income can be earned from tasks (or
requests) done by this service. In our model, services can decide
to compete to get a task from the master agent or to cooperate
with other services within a given collaborative network (the way
a collaborative network is set by a leader is based on the
cooperative services reputation and their QoS parameters that
should coincide with the required QoS). Therefore we define two
types of service strategies. First, when a service has higher
level of confidence based on its growth factor, it can compete to
get a task from the master and adopts the competitive strategy.
Second, when the service agent has a lower level of confidence
that it does not feel capable to compete, it waits for some other
services to cooperate with to perform some tasks \footnote{Through
the report, requests or tasks are supposed to be decomposable.},
and thus it adopts the cooperative strategy. Services estimate the
outcome of all the strategies and choose one of them accordingly.
This decision is not static but can change over time so service
agents can switch from one strategy to the other, and this dynamic
attitude is referred to as coopetition.

@@

\subsection{Coalition Formation and Stability}

@@

For the \emph{optimal core} method, we have used the well known
\emph{$\epsilon$-core} method as the taxation method to relax the
core condition to help communities attract web services. We have
assigned $\epsilon$ to 15\% of total community worth, which means
$\epsilon = 0.15 \times v(C)$. This allows subsets of the
coalition to gain maximum 15\% of $v(C)$.
%In the \emph{optimal
%$\epsilon$-core} method, we capped the coalition size to 25 web
%services, since the method is computationally intractable as the
%number of web services increases. In fact, given the machine
%configuration we used in our experiments, the maximum number we
%could run for this method is 25, which is very realistic if we
%consider the real airlines coalitions (the three well known
%coalitions have respectively 28, 19, and 13 members). In the other
%methods, there were no cap on size of the community and we had
%communities of size 160 web services at some points, as discussed
%above.
In the experiments, our \emph{Depth-1 Convex-Checker} and
\emph{Depth-2 Convex-Checker} methods generate results instantly
(0.01ms in Java millisecond time unit granularity) in our machines
since their runtime with respect to the size of input (number of
web services) is $O(n)$ and $O(n^2)$ respectively. This shows that
the algorithms are efficient and the system is easily scalable. In
this scenario, our community receives 130 tasks from users on
average per iteration. These tasks are randomly generated.
%These tasks are about flight booking and
%are expected to be performed by the community. They are randomly
%generated using a poisson distribution (having 130 as parameter).
Depending on community task queue and the assigned web services'
quality metrics the task will be performed with some qualities.
The community, after the task distribution process on each
iteration, will reevaluate QoS metrics of its members and can
check for new membership requests. Web services may join or leave
the community between iterations. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to the optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing
well.

@@

\subsection{Coopetitive Behavior}\label{sb:resutlscoop}

In this section, the objective is to investigate the effectiveness of the proposed strategic system in Section \ref{s:coop}.
We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this report (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive).
%The proposed model's
%reasoning mechanism allows services to make decisions that
%maximize their utilities, so that if the service cannot compete,
%the procedure would suggest to collaborate, which is better than
%competing and failing to obtain the task. In this case, the service stays idle but
%still pays the community membership fee, which means losing
%utility. The developed strategic decision making mechanism leads
%some service agents to follow cooperative strategies that overall
%maintain an optimal community budget. In the same figure, we
%observe the cumulative budget of a community where services follow
%random interacting strategies. The outcome is clearly lower
%because services at each run randomly decide over their acting
%strategies. This potentially influences the community budget
%because a low quality service if randomly selects to follow the
%competitive strategy, it will fail to perform a task with high QoS
%requirements.

### 2014-03-05 seminar/seminar_report/chapter5.tex
changes

@@

@@

\item \textbf{Winter 2015: }Thesis work and PhD Defense.
%\item Developing an open source, Java based Tool, with UI for
%solving Core and Shapely solution concepts based on different
%input valuation functions.
\end{itemize}

@@

\subsection {Publications }

    \begin{enumerate}
        \small{
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Community Formation for Web Services.''} Accepted at IEEE Transactions on Services Computing, Feb. 2014, IEEE. (Impact factor: 2.46)
        \item E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, B. Khosravifar, H. Otrok, \emph{``To Compete or to Cooperate? This is the Question in Communities of Autonomous Services.''} In the Journal of Expert Systems and Applications, Feb. 2014, Elsevier. (Impact factor: 1.854, 5-year:  2.339)
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Coalition Formation for Web Services. In the 10th''} IEEE  International Conference on Services Computing (SCC 2013), Santa Clara Marriott, CA, USA, June 27-July 2, 2013
        \item B. Khosravifar, M. Alishahi, E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, H. Otrok, \emph{``Analyzing Coopetition Strategies of Services within Communities''}. In the 10th International Conference on Service Oriented Computing, (ICSOC 2012), Shanghai, China, Nov. 2012
        }
    \end{enumerate}

>>>>

\section {Conclusion}

@@

We also proposed a coopetitive strategic model to analyze
the interacting behavior of intelligent services that are active within communities.
We considered two acting strategies where service agents expect different sort of payoffs:
(1) competitive strategy where the service claims that it can accomplish a task,
and therefore can take the responsibility over the service consumer satisfaction; and (2)
cooperative strategy where the service does not take the responsibility to accomplish
the task and only cooperates with competitive peers. Our proposed model advances the
state-of-the-art in cooperative systems by enabling intelligent agent-based services to
effectively choose their interacting strategies that lead to optimal outcomes. The proposed
framework provides a reasoning technique that service agents can use to increase
their overall obtained utilities. The theoretical results presented in this research work are also
backed by simulation results using a real services dataset. Those results showed that
our model outperforms existing competitive and random coopetitive strategies.

@@

\item \textbf{Winter 2015: }Thesis work and Ph.D. Defense.
%\item Developing an open source, Java based Tool, with UI for
%solving Core and Shapely solution concepts based on different
%input valuation functions.
\end{itemize}

@@

\section {Publications }

    \begin{enumerate}
        \small{
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Community Formation for Web Services.''} Accepted at IEEE Transactions on Services Computing, Feb. 2014, IEEE. (Impact factor: 2.46)
        \item E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, B. Khosravifar, H. Otrok, \emph{``To Compete or Cooperate? This is the Question in Communities of Autonomous Services.''} In the Journal of Expert Systems and Applications, Feb. 2014, Elsevier. (Impact factor: 1.854, 5-year:  2.339)
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Coalition Formation for Web Services. In the 10th''} IEEE  International Conference on Services Computing (SCC 2013), Santa Clara Marriott, CA, USA, June 27-July 2, 2013
        \item B. Khosravifar, M. Alishahi, E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, H. Otrok, \emph{``Analyzing Coopetition Strategies of Services within Communities''}. In the 10th International Conference on Service Oriented Computing, (ICSOC 2012), Shanghai, China, Nov. 2012
        }
    \end{enumerate}
